Glyph-maps for Visually Exploring Temporal Patterns in Climate Data and Models

### 2012-03-03 revision/paper.tex
Legends for scaling
Legends for generalisations

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.5\linewidth]{month-rescale-none}%
  % \includegraphics[width=0.5\linewidth]{month-rescale-max}%
  \includegraphics[width=0.5\linewidth]{month-rescale01}
  \caption{Smoothed de-seasonalized daily temperature glyph-map. (Left)
globally scaled, (right) locally scaled.}
  \label{fig:scaling}
\end{figure}

@@

  \caption{Glyph-map showing (left) scatterplot of temperature vs high-cloud and (right) smoothed (loess) curve fit to each location. The relationship between these two variables varies considerably over the spatial domain. }
  \label{fig:cloud}
\end{figure}

>>>>

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.5\linewidth]{month-rescale-none}%
  % \includegraphics[width=0.5\linewidth]{month-rescale-max}%
  \includegraphics[width=0.5\linewidth]{month-rescale01}

  \includegraphics[width=0.33\linewidth]{month-rescale-legend}

  \caption{Smoothed de-seasonalized daily temperature glyph-map. (Top-left)
globally scaled, (Top-right) locally scaled. (Bottom) Legend showing ranges of individual glyphs.}
  \label{fig:scaling}
\end{figure}

@@

  \includegraphics[width=0.33\linewidth]{nasa-scat-legend}%
  \hspace{0.17\linewidth}%
  \includegraphics[width=0.33\linewidth]{nasa-loess-legend}

  \caption{Glyph-map showing (top-left) scatterplot of temperature vs high-cloud and (top-right) smoothed (loess) curve fit to each location. The relationship between these two variables varies considerably over the spatial domain. (Bottom) Legends show overall patterns and scales.}
  \label{fig:cloud}
\end{figure}
